The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-03-20 paper/ms.tex
introduction

Since then, other examples of Bullet-like systems have been found; 
MACS J0025.4-1222 \citep{Bradac2008}, Abell 2744 \citep{Merten2011},
DLSCL J0916.2+2951 \citep{Dawson2012}, ZwCl 1234.0+02916
\citep{Dahle2013}. Recently \citep{Gastaldello} observed a baryonic-DM
displacement if $124\pm 20$ kpc in \bullg, a group-like system with a total
mass $2.4\pm 0.6 \times 10^{14}$\Msun. Systems of this mass are
$\sim10$ times more abundant than cluster systems in the mass range of
the Bullet Cluster $>10^{15}$\hMsun, this opens up the possibility of
observationally finding bullet groups in a fair amount to impose
constraints on $\Lambda$CDM.

However, a greater abundance of small mass systems has to be weighted
by the probability of having a merger and 
presenting a large displacement between the DM and baryonic
components. These two conditions (merger rates, maximum possible
displacement) are a funcion of DM halo mass in $\Lambda$CDM
cosmologies.  Such study has been performed for clusters but not for
lower mass systems \citep{ForeroRomero2010}. The existence of objects
like \bullg\ and observational campaigns like the Strong Lensing Legacy
Survey (SL2S) \citep{Cabanac2007,More2012} open up the possibility of finding
multi-modal dark matter distributions in the group mass range.

In this Letter we compute the abundance of group-like dark
matter halos with a multi-modal morphology that also might present a
DM-baryon displacement. To this end we use a N-body cosmological
simulation with such a resolution that allows us to identify
multi-modal dark matter distributions in hosts with circular velocities
larger than $300$\kms.

This Letter is organized as follows. In Section
\ref{sec:simulation} we present the simulation and the halo catalogs
used in this work. We continue in Section \ref{sec:setup} with the
geometry of the problem at hand and the measurements setup. Next in
Section \ref{sec:results} we present our results and observational
perspectives to finally conclude in Section \ref{sec:conclusions}.

>>>>

Since then, other examples of Bullet-like systems have been found; 
MACS J0025.4-1222 \citep{Bradac2008}, Abell 2744 \citep{Merten2011},
DLSCL J0916.2+2951 \citep{Dawson2012}, ZwCl 1234.0+02916
\citep{Dahle2013}. Recently \citep{Gastaldello} observed a DM-baryon
displacement of $87\pm 14$\hkpc and a DM-DM separation of $186\pm
30$\hkpc in \bullg, a group-like system with a total
mass $2.4\pm 0.6 \times 10^{14}$\Msun found in the the Strong Lensing
Legacy Survey (SL2S) sample \citep{Cabanac2007,More2012}.

Groups around this mass are $\sim10$ times more abundant than clusters
in the mass range of the Bullet Cluster $>10^{15}$\hMsun. This 
should open up the possibility of finding Bullet Groups in large
numbers to test $\Lambda$CDM. However, a larger abundance of small
mass systems has to be weighted by the probability of being in a
merger and  presenting a large displacement between the DM and
baryonic components.  These two conditions (merger rates, maximum
possible displacement) are a funcion of DM halo mass in $\Lambda$CDM
cosmologies.  A detailed statistical study to estimate the abundance
of Bullets has been performed for clusters but not for lower mass
systems \citep{ForeroRomero2010}.

In this Letter we extend such study for systems in the group mass
scale. We measure the abundance of DM systems with with a multi-modal
morphology (large DM-DM displacements) and estimate the amount of
systems with a Bullet configuration  (large DM-baryon
displacements). To this end we use a high resolution N-body
cosmological simulation (Bolshoi) that allows us to find  multi-modal
dark matter distributions in hosts with circular velocities larger
than $300$\kms ($\sim 1.0\times 10^{13}\hMsun$).

This Letter is organized as follows. In Section
\ref{sec:simulation} we present the simulation and the halo catalogs
used in this work. We continue in Section \ref{sec:setup} with the
geometry of the problem at hand and the measurement setup. Next in
Section \ref{sec:results} we present our results and observational
perspectives to finally conclude in Section \ref{sec:conclusions}.
